Apparent preferences for cognitive effort fade when multiple forms of effort

### 2020-11-19 Cost_manuscript.Rmd
tweaks

>>>>

  The present findings provide theoretical advances as well as practical implementations. Talk clinical and practical. Practical could be motivating people to pursue challenges that produce desirable outcomes, like work, exercise etc.  Much of the literature on the value of effort has suggested that it can be triggered by careful reward schedules. This doesn't always do (Eisenberger, Inzlicht). There is also the idea that training in certain tasks will have generaliing effects, which are not always true (Kable). We highlight an outcome-independent feature that is phenomenologically common (time sensitivity), and potentially easy to implement.
